Robotic Cart System

### 2021-05-03 parts/40-algorithms.tex
Updates to final report based on feedback from Dr. Miah

%======================================================================
\chapter{Algorithms}
\label{ch: Chapter4}
%======================================================================

%----------------------------------------------------------------------
\section{Robot Model}\label{sec:robotModel}
%----------------------------------------------------------------------
The robot used in this project was a differential drive mobile robot, which has two drive wheels and a caster wheel for balance. The robot turns by applying different speeds to the left and right wheels. As shown in Fig. \ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance between the wheels is $L$. The pose of the robot is given by the $x$-coordinate ($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in Fig. \ref{fig:robotPose}.
\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotGeometry.png}
        \caption{Robot Geometry}
        \label{fig:robotGeometry}
    \end{subfigure}%
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotPose.png}
        \caption{Robot Pose}
        \label{fig:robotPose}
    \end{subfigure}
    \caption{Robot Model Parameters}
    \label{fig:robotModelParameters}
\end{figure}

\vspace*{12pt}
\noindent
Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively). These speeds must be converted into left and right wheel speeds. The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
To control DC motors in this way, the relationship between duty cycle and angular speed must be determined. Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.

>>>>

%======================================================================
\chapter{Localization and Navigation}
\label{ch: Chapter4}
%======================================================================

This chapter illustrates the localization and navigation algorithms for the mobile cart to operate in an indoor/outdoor environment. The proposed robotic cart was modeled as a differential drive mobile robot (DDMR). The direction and distance of the remote relative to the cart are determined using a localization algorithm. This distance and angle are then passed to a navigation algorithm which calculates and applies the wheel speeds to move the robot toward the remote.

%----------------------------------------------------------------------
\section{Robot Model}\label{sec:robotModel}
%----------------------------------------------------------------------
The robot used in this project was a differential drive mobile robot, which has
two drive wheels and a caster wheel for balance. The robot turns by applying
different speeds to the left and right wheels. As shown in Fig.
\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance
between the wheels is $L$. The pose of the robot is given by the $x$-coordinate
($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in
Fig. \ref{fig:robotPose}. %
%
\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotGeometry.png}
        \caption{Robot Geometry}
        \label{fig:robotGeometry}
    \end{subfigure}%
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotPose.png}
        \caption{Robot Pose}
        \label{fig:robotPose}
    \end{subfigure}
    \caption{Robot Model Parameters}
    \label{fig:robotModelParameters}
\end{figure}
%

Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively). These speeds must be converted into left and right wheel speeds. The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
To control DC motors in this way, the relationship between duty cycle and angular speed must be determined. Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.
